\documentclass[SE,lsstdraft,STR,toc]{lsstdoc}
\usepackage{geometry}
\usepackage{longtable,booktabs}
\usepackage{enumitem}
\usepackage{arydshln}

\input meta.tex

\providecommand{\tightlist}{
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\def\milestoneName{Ccw Functional Re-Verification}
\def\milestoneId{LVV-P64}
\def\product{SIT-COM Integration}

\setDocCompact{true}

\title{ LVV-P64 Ccw Functional Re-Verification Test Plan and Report}
\setDocRef{\lsstDocType-\lsstDocNum}
\date{\vcsdate}
\setDocUpstreamLocation{\url{https://github.com/lsst/lsst-texmf/examples}}
\author{ Austin Roberts }

\input history_and_info.tex


\setDocAbstract{
This is the test plan and report for LVV-P64 (Ccw Functional Re-Verification),
an LSST milestone pertaining to the System Engineering Subsystem.
}


\maketitle

\section{Introduction}
\label{sect:intro}


\subsection{Objectives}
\label{sect:objectives}

The objective of this test plan is to re-verify the functional
requirements of the Camera Cable Wrap's hardware and software, after
shipment from the vendors facility to the Summit, as defined in \citeds{LTS-218}.
This test campaign will only exercise the functionality that was
executed previously and meets the following criteria:

\begin{itemize}
\tightlist
\item
  Only requires the CCW to be operable
\item
  Only requires the vendors EUI software and hardware via local control
\item
  Only requires a laser tracker
\item
  Does \textbf{NOT} require the Camera Rotator to be loaded with the
  camera simulated mass or actual camera hardware
\end{itemize}

The hardware functional requirements were previously verified during the
test campaign by the vendor at the vendors facility and accepted by LSST
during the Factory Acceptance Test
review.\\[2\baselineskip]\textbf{NOTE:~} This re-verification is the
responsibility of the vendor. This Test Plan and Report is to capture
this event and it's results utilizing the LSST Verification
Architecture, but may not have detailed test steps defined in the Test
Cases of this test campaign.



\subsection{System Overview}
\label{sect:systemoverview}

The primary function of the Camera Cable Wrap is to rotate in a
synchronous fashion with the Camera Rotator to prevent the utilities
from getting damaged.


\subsection{Document Overview}
\label{sect:docoverview}

This document was generated from Jira, obtaining the relevant information from the 
\href{https://jira.lsstcorp.org/secure/Tests.jspa#/testPlan/LVV-P64}{LVV-P64}
~Jira Test Plan and related Test Cycles (
  \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCycle/LVV-C112}{LVV-C112}
).

Section \ref{sect:intro} provides an overview of the test campaign, the system under test (\product{}), the applicable documentation, and explains how this document is organized.
Section \ref{sect:configuration}  describes the configuration used for this test.
Section \ref{sect:personnel} describes the necessary roles and lists the individuals assigned to them.
%Section \ref{sect:plannedtestactivities} provides the list of planned test cycles and test cases, including all relevant information that fully describes the test campaign.

Section \ref{sect:overview} provides a summary of the test results, including an overview in Table \ref{table:summary}, an overall assessment statement and suggestions for possible improvements.
Section \ref{sect:detailedtestresults} provides detailed results for each step in each test case.

The current status of test plan LVV-P64 in Jira is \textbf{ Draft }.

\subsection{References}
\label{sect:references}
\renewcommand{\refname}{}
\bibliography{lsst,refs,books,refs_ads,local}
\section{Test Configuration}
\label{sect:configuration}

\subsection{Data Collection}

  Observing is not required for this test campaign.

\subsection{Verification Environment}
\label{sect:hwconf}
  The Camera Cable Wrap will be verified in a climate controlled
environment on the 3rd floor of the Summit Facility integrated with the
Camera Rotator on the Camera Cart.


  \subsection{Entry Criteria}
  In order to test the Camera Cable Wrap functionality, the following
criteria must be met first:

\begin{itemize}
\tightlist
\item
  All utilities and electrical connections are hooked up and allow the
  Camera Cable Wrap to be powered on and controlled
\item
  The EFD must be set up to be able to store events and telemetry data
\end{itemize}


  \subsection{Exit Criteria}
  In order for this event to be considered complete, the following
criteria must be met:

\begin{itemize}
\tightlist
\item
  Raw test data, events, and telemetry have been saved for the Camera
  Cable Wrap.
\item
  All test data has been analyzed and post processed.
\item
  The vendor has produced and provided LSST with a Test Report detailing
  all findings.
\item
  The vendor's Test Report has been attached to this Test Plan.
\item
  A summary of the results of the test campaign has been captured in the
  Overall Assessment and Recommended Improvements fields of this Test
  Plan
\item
  A link to the verification artifacts used to produce the summary of
  results has been populated in the Verification Artifacts field of this
  Test Plan
\item
  Any failures have been captured in the
  \href{https://jira.lsstcorp.org/projects/FRACAS/issues/}{FRACAS}
  project
\end{itemize}



\newpage
\section{Personnel}
\label{sect:personnel}

The personnel involved in the test campaign is shown in the following table.

\begin{longtable}{p{3cm}p{3cm}p{3cm}p{6cm}}
\hline
\multicolumn{2}{r}{Test Plan (LVV-P64) owner:} &
\multicolumn{2}{l}{\textbf{ Austin Roberts } }\\\hline
\multicolumn{2}{r}{ LVV-C112 owner:} &
\multicolumn{2}{l}{\textbf{
    Undefined
}
} \\\hline
\textbf{Test Case} & \textbf{Assigned to} & \textbf{Executed by} & \textbf{Additional Test Personnel} \\ \hline
\href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1590}{LVV-T1590}
& {\small Kevin Siruno } & {\small  } &
\begin{minipage}[]{6cm}
\smallskip
{\small The Summit facility's 3rd floor requires the following:

\begin{itemize}
\tightlist
\item
  Safety Shoes
\item
  Eye Protection
\item
  Hard Hat
\item
  Safety Vest
\end{itemize}
 }
\medskip
\end{minipage}
\\ \hline
\end{longtable}

\newpage

\section{Test Campaign Overview}
\label{sect:overview}

\subsection{Summary}
\label{sect:summarytable}

\begin{longtable}{p{2cm}p{2.5cm}p{9cm}p{2.5cm}}
\toprule
\multicolumn{3}{l}{ Test Plan {\bf LVV-P64: CCW Functional Re-verification
 }} & Draft \\\hline

  \multicolumn{3}{l}{ Test Cycle {\bf LVV-C112: CCW Functional Re-verificaiton
 }} & Not Executed \\\hline

  {\bf \footnotesize test case} & {\bf \footnotesize status} & {\bf \footnotesize comment} & {\bf \footnotesize issues} \\\toprule

    \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1590}{LVV-T1590}
    & Not Executed &
    \begin{minipage}[]{9cm}
    \smallskip
    
    \medskip
    \end{minipage}
    &
    \\\hline
\caption{Test Results Summary}
\label{table:summary}
\end{longtable}

\subsection{Overall Assessment}
\label{sect:overallassessment}

Not yet available.

\subsection{Recommended Improvements}
\label{sect:recommendations}

Not yet available.

\newpage
\section{Detailed Test Results}
\label{sect:detailedtestresults}

\subsection{Test Cycle LVV-C112 }

Open test cycle {\it \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testrun/LVV-C112}{CCW Functional Re-verificaiton
}} in Jira.

CCW Functional Re-verificaiton
\\
Status: Not Executed

This purpose of this test cycle is to run initial tests on the summit to
re-verify the CCW as previously tested at the vendor's facility.


\subsubsection{Software Version/Baseline}
Not provided.

\subsubsection{Configuration}
Not provided.

\subsubsection{Test Cases in LVV-C112 Test Cycle}

\paragraph{Test Case LVV-T1590 - CCW Functional Re-verification
 }\mbox{}\\

Open  \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1590}{\textit{ LVV-T1590 } }
test case in Jira.

The purpose of this test case is to re-verify the functional
requirements of the CCW that the vendor had initially tested at their
facility, as defined by \citeds{LTS-218}. This test campaign will only exercise
the functionality that was previously executed and meets the following
criteria:

\begin{itemize}
\tightlist
\item
  Only requires the CCW Utility (electric, network \& software) to be
  hooked up
\item
  Only requires a HHD to control the EUI
\item
  Does \textbf{NOT} require to be connected to the actual camera
  hardware
\end{itemize}

\textbf{{This will be a placeholder for any documentation that shows
which requirements have been verified. We will attach any documents from
any testing done previously and the procedure that the vendor followed
to obtain the results of the previous tests.}}

\begin{itemize}
\tightlist
\item
  \textbf{{Ask Andrew Heyer if he has procedural documents regarding:}}

  \begin{itemize}
  \tightlist
  \item
    \textbf{{how to do the visual checking of the CCW to verify that it
    made it to the summit undamaged}}
  \item
    \textbf{{a detailed plan of the series of tests for the CCW via the
    EUI}}
  \item
    {\textbf{Detailed plan of the reduced tests}}
  \end{itemize}
\end{itemize}


\textbf{ Preconditions}:\\
\textbf{{-Look for Summit Tasks that relate to assembly/preparation}}

\begin{itemize}
\tightlist
\item
  \textbf{{CCW Aux Control Cabinet Prep}}

  \begin{itemize}
  \tightlist
  \item
    \textbf{{drilling hole in cabinet}}
  \item
    \textbf{{connecting Camera Cable Wrap Auxiliary Control Computer to
    monitor}}
  \item
    {\textbf{wiring changes to new computer (add a breaker, swap for
    larger transformer, modify ethernet wiring)}}
  \item
    \textbf{{install CCW Aux Control Computer}}
  \end{itemize}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{\textbf{{CCW Aux Control Cabinet Check}}}

  \begin{itemize}
  \tightlist
  \item
    \textbf{{check to see that no short circuits are occurring}}
  \item
    \textbf{{Check to see if cables are connected properly and signals
    are OK}}
  \end{itemize}
\end{itemize}


Execution status: {\bf Not Executed }

Final comment:\\


Detailed steps results:

\begin{longtable}{p{1cm}p{15cm}}
\hline
{Step} & Step Details\\ \hline
1 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
\smallskip

\medskip }
\end{minipage}
\\ \cdashline{2-2}


 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

2 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
\smallskip
In move mode, command 25deg movement to the CCW and no movement to the
camera rotator.

\medskip }
\end{minipage}
\\ \cdashline{2-2}


 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

3 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
\smallskip
Use the analysis for the measured average motor current from the 8-hour
test data and calculate the average heat during slewing.~

\medskip }
\end{minipage}
\\ \cdashline{2-2}


 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip
The heat is calculated to be no more than 50W of heat.

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
\smallskip

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

\end{longtable}


\input{appendix.tex}
\end{document}
